---
title: "Animal Crossing Data"
output: html_document
---

```{r, message=FALSE}
#Loading needed packages
library(mdsr)
library(tidyverse)
library(gapminder)
library(data.table)
library(ngram)
library(gutenbergr)
library(tidytext)
```


```{r, message=FALSE, warning= FALSE}
#Load datasets

critic <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/critic.tsv')
user_reviews <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/user_reviews.tsv')
items <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/items.csv')
villagers <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/villagers.csv')

View(critic)
View(user_reviews)
View(items)
View(villagers)
```

*Villagers*
**Question: Are there more of a certain type of personality or is it evenly distributed?**
```{r}

villagers %>% 
  count(personality) %>% 
  arrange(desc(n))

```

Based of the new table, it looks like there doesn't seem to be an even distribution of personalities. Let's take a look at a graph:

**Creating a graph to show the distribuition of personalities**
```{r}
villagers %>% 
  count(personality) %>% 
  arrange(desc(n)) %>% 
  ggplot(aes(x = fct_reorder(personality,n), y = n))+
  geom_col(aes(fill = personality), alpha = 0.6)+
  labs(x = "Personality", y = "Number of Villagers")+
  geom_label(aes(label = n), size = 4, nudge_y = 7) +
  theme_minimal()+
  theme(legend.position = "none")+
  coord_flip()
```

According to the graph, it looks like the most common personality trait is lazy and the least common personality trait is uchi (uchi is a female villager personality. Ther are very caring and not too vain towards the villagers).

**Question: What is the distribution of personalities amongst differnt types of animals?**

First let's take a look at the distribution of species:
```{r}
villagers %>% 
  count(species) %>% 
  arrange(desc(n)) %>% 
  ggplot(aes(x = fct_reorder(species,n), y = n))+
  geom_col(aes(fill = species), alpha = 0.6)+
  labs(x = "Species", y = "Number of Villagers")+
  theme_minimal()+
  theme(legend.position = "none")+
  coord_flip()

```

It seems the 5 most common animals are: cats, rabbits, squirrels, frogs, and ducks.
Let's take a look into the personality districution of the most popular animal: cats!

```{r}
villagers_cats = villagers %>% 
  filter(species == "cat") %>% 
  count(personality) %>% 
  arrange(desc(n)) %>% 
  ggplot(aes(x = fct_reorder(personality, n), y = n))+
  geom_col(aes(fill = personality), alpha = 0.6)+
  labs(x = "Personality", y = "Number of Cat Villagers")+
  theme_minimal()+
  theme(legend.position = "none")+
  coord_flip()

villagers_cats
  
```

Now let's take a look at the other animals: rabbits, squirrels, frogs, and ducks!
```{r}
villagers_most_common = villagers %>% 
  filter(species %in% c("rabbit","squirrel","frog","duck")) %>% 
  group_by(species) %>% 
  count(personality) %>% 
  arrange(desc(n)) %>% 
  ggplot(aes(x = fct_reorder(personality, n), y = n))+
  geom_col(aes(fill = personality), alpha = 0.6)+
  labs(x = "Personality", y = "Number of Villagers")+
  geom_label(aes(label = n), size = 2.5, nudge_y = 7) +
  theme_minimal()+
  theme(legend.position = "none")+
  coord_flip()+
  facet_wrap(~species)

villagers_most_common
```

It looks like the type of personality each villager has based off of what type of aniaml they are is completly random.
