---
title: "Animal Crossing Data"
output: html_document
---

```{r,echo=FALSE, warning = FALSE, message = FALSE}
# Load any R Packages you may need
library(tidyverse)
library(mdsr)
library(tidyverse)
library(gapminder)
library(data.table)
library(ngram)
library(gutenbergr)
library(tidytext)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
critic <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/critic.tsv')
user_reviews <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/user_reviews.tsv')
items <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/items.csv')
villagers <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/villagers.csv')
```

```{r, echo = FALSE, warning = FALSE, message = FALSE}
View(critic)
View(user_reviews)
View(items)
View(villagers)
```

# Escaping the Real World to Run Errands in a Virtual Game

With the world currently in quarantine, many people are finding a way to kill time with Nintendo's latest release: "Animal Crossing: New Horizons"!
In this game, players escape to a deserted island where they beomce indebted to Tom Nook, a tanuki capitalist overlord who holds all of your mortgages. It is up to the player to run errands and to collect items such as fruits, insects and fish to sell to the tanuki in hopes of ever repaying their debt and earning new upgrades to make the island more beautful. In this game, you are in control of the isalnd and have the ability to design and decorate it in any way you like! You can also socialize with villagers who can give you new crafting recipes and gifts if you befriend them, or you can be mean and force them to leave the island if you don't like their personality.

As you might have figured out by now, this blog will be focusing on Animal Crossing data!

The data set we found on Tidy Tuesday has 4 differnt sets within it: Items, Villagers, Critic reviews, and User reviews. In this blog, we wil breaking up into differnt sections to explore each data set to answer some questions we may have and what we can discover from these datasets.

Let's start of with the items data!

## Items

While looking over the items data set, we noticed that there are some duplicates of each item. So before we start working with the data, lets do some tidying up!

### Mini Tidy Data Tutorial
In Animal Crossing, there are many differnet items in the game. But for the purpose of this blog and to make our lives easier, we will be focusing on the items that are categorized as furniture. 

Here we will filter out the table to focus on furniture:
```{r}
furniture_items = items %>%
  filter(category == "Furniture") %>%
  select(num_id, id, name, sell_value, buy_value)

#next use mutate to create a new column for the furniture_set and extract it from the part of the id before the - (use regex)

furniture_items
```

Now let's move on to the villager data!

## Villagers

Villagers in animal crossing are animals, and there are many different types of animals in the game, 35 differnet species to be exactt! Each villager also has their own personality which can be categorized into 8 different types (4 female, 4 male): Normal, Peppy, Snooty, Uchi (sisterly), Cranky, Jock, Lazy, and Smug.

Let's take a look and see if the differnt personality types are evenly distributed amongst villagers or if ther are more common personalities compared to others.

**Question: Are there more of a certain type of personality or is it evenly distributed?**
```{r}

villagers %>% 
  count(personality) %>% 
  arrange(desc(n))

```

Based of the table, it looks like there doesn't seem to be an even distribution of personalities. Let's take a look at a graph to get a better visualization:

**Creating a graph to show the distribuition of personalities**
```{r}
villagers %>% 
  count(personality) %>% 
  arrange(desc(n)) %>% 
  ggplot(aes(x = fct_reorder(personality,n), y = n))+
  geom_col(aes(fill = personality), alpha = 0.6)+
  labs(x = "Personality", y = "Number of Villagers")+
  geom_label(aes(label = n), size = 4, nudge_y = 7) +
  theme_minimal()+
  theme(legend.position = "none")+
  coord_flip()
```

According to the graph, it looks like the most common personality trait is lazy and the least common personality trait is uchi (uchi is a female villager personality. They are very caring and not too vain towards the villagers).

Another thing to notice from the graph is that it appears as though the distribution  pattern amongst the personalities for male and female are the same. To see this more clearly, let's take a look at the same grapgh but instead have it split betwen male and female:

**female**
```{r}
personality_female = villagers %>% 
  filter(gender == "female") %>% 
  group_by(gender) %>% 
  count(personality) %>% 
  arrange(desc(n)) %>% 
  ggplot(aes(x = fct_reorder(personality, n), y = n))+
  geom_col(aes(fill = personality), alpha = 0.6)+
  labs(x = "Personality", y = "Number of Villagers")+
  geom_label(aes(label = n), size = 2.5, nudge_y = 7) +
  theme_minimal()+
  theme(legend.position = "none")+
  coord_flip()+
  facet_wrap(~gender)

personality_female
```
**male**
```{r}
personality_male = villagers %>% 
  filter(gender == "male") %>% 
  group_by(gender) %>% 
  count(personality) %>% 
  arrange(desc(n)) %>% 
  ggplot(aes(x = fct_reorder(personality, n), y = n))+
  geom_col(aes(fill = personality), alpha = 0.6)+
  labs(x = "Personality", y = "Number of Villagers")+
  geom_label(aes(label = n), size = 2.5, nudge_y = 7) +
  theme_minimal()+
  theme(legend.position = "none")+
  coord_flip()+
  facet_wrap(~gender)

personality_male
```

When you look at the two graphs you can see how there is always the most common trait, then 2 common traits which arent that far off from the most common trait, and then the least common trait falls behind in numbers by quite a bit.

Now let's take a look at how the personalities are distributed in each species of animal:

**Question: What is the distribution of personalities amongst differnt types of animals?**

First let's take a look at the distribution of species:
```{r}
villagers %>% 
  count(species) %>% 
  arrange(desc(n)) %>% 
  ggplot(aes(x = fct_reorder(species,n), y = n))+
  geom_col(aes(fill = species), alpha = 0.6)+
  labs(x = "Species", y = "Number of Villagers")+
  theme_minimal()+
  theme(legend.position = "none")+
  coord_flip()

```

There are 35 differnt species, and having to look at 35 differnt graphs can be quite hectic, so to make our lives easier let's focus on the top 5 animals. The 5 most common animals are: cats, rabbits, squirrels, frogs, and ducks.

First let's take a look into the personality distribution of the most popular animal: cats!
**Cat Personality**
```{r}
villagers_cats = villagers %>% 
  filter(species == "cat") %>% 
  count(personality) %>% 
  arrange(desc(n)) %>% 
  ggplot(aes(x = fct_reorder(personality, n), y = n))+
  geom_col(aes(fill = personality), alpha = 0.6)+
  labs(x = "Personality", y = "Number of Cat Villagers")+
  theme_minimal()+
  theme(legend.position = "none")+
  coord_flip()

villagers_cats
  
```

Now let's take a look at the other animals: rabbits, squirrels, frogs, and ducks!
```{r}
villagers_most_common = villagers %>% 
  filter(species %in% c("rabbit","squirrel","frog","duck")) %>% 
  group_by(species) %>% 
  count(personality) %>% 
  arrange(desc(n)) %>% 
  ggplot(aes(x = fct_reorder(personality, n), y = n))+
  geom_col(aes(fill = personality), alpha = 0.6)+
  labs(x = "Personality", y = "Number of Villagers")+
  geom_label(aes(label = n), size = 2.5, nudge_y = 7) +
  theme_minimal()+
  theme(legend.position = "none")+
  coord_flip()+
  facet_wrap(~species)

villagers_most_common
```

It looks like the type of personality each villager has based off of what type of aniaml they are is completly random.


Since many people are playing Animal Crossing, ,lets take a look to see what their opionons are and compare them to what critics think.

## Critic and User Reviews

Since many people are playing Animal Crossing, ,lets take a look to see what their opionons are and compare them to what critics think.

### Anlayzing the Reviews

With the critic and user reviews, we can analyze some text data via sentiment analysis to determine whether a review was positive or negative. 

**critic**

```{r}
critic_reviews_tidy = critic %>%
  unnest_tokens(output = word, input = text)

critic_sentiment = critic_reviews_tidy %>%
  inner_join(get_sentiments("bing"), by = c("word" = "word"))

critic_sentiment

sentiment_counts = critic_sentiment %>%
  count(word, sentiment, sort = TRUE)
sentiment_counts %>%
  group_by(sentiment) %>%
  top_n(10, wt = n) %>%
  ggplot(aes(x = fct_reorder(word, n), y = n, 
             fill = sentiment)) + 
  geom_col() + 
  facet_wrap( ~ sentiment, scales = "free_y") + 
  labs(x = "", y = "Contribution to sentiment", 
       title = "Sentiment Analysis of Critic Reviews of Animal Crossing") +
  theme_bw() + 
  theme(legend.position = "none") +
  coord_flip()
```

**User Reviews**
```{r}
user_reviews_tidy = user_reviews %>%
  unnest_tokens(output = word, input = text)

user_sentiment = user_reviews_tidy %>%
  inner_join(get_sentiments("bing"), by = c("word" = "word")) 

user_sentiment

sentiment_counts = user_sentiment %>%
  count(word, sentiment, sort = TRUE)
sentiment_counts %>%
  group_by(sentiment) %>%
  top_n(10, wt = n) %>%
  ggplot(aes(x = fct_reorder(word, n), y = n, 
             fill = sentiment)) + 
  geom_col() + 
  facet_wrap( ~ sentiment, scales = "free_y") + 
  labs(x = "", y = "Contribution to sentiment", 
       title = "Sentiment Analysis of User Reviews of Animal Crossing") +
  theme_bw() + 
  theme(legend.position = "none") +
  coord_flip()
```

### Comparing the Ratings

**Average User Rating**

```{r}
user_reviews %>% 
  summarize(mean_rating = mean(grade, na.rm = TRUE))
```

**Average Critic Rating**
```{r}
critic %>% 
  summarize(mean_rating = mean(grade, na.rm = TRUE))
```

It appears as though user's arent too happy with the game compared to the critic reviews. A good explanation of that would be the wave of new players to the game. For those who don't know, animal crossing is meant to be a single player game in which there is only one world per console/device. This has always been the way of Animal Crosing and old players of the game (who have played older versions of Animal Crossing) already know this. However, due to the hype that Animal Crossing: New Horizons recieved, it attracted a lot of new players. Unfortunatley, new players learned the hard way that they can only have one island per console and a lot of people, especially parents, are not happy with that... but it is what it is. 
*Animal Crossing is a great game, some people are just salty*